Concentration of Maxima and Fundamental Limits in High-Dimensional Testing and Inference

### 2021-04-04 4.exact_support_recovery/exact_support_recovery.tex
many changes... Chapter 4 intro WIP

We focus on exact support recovery problems in this chapter, and generalize the results we obtained in Chapter \ref{chap:phase-transitions} to additive error models with much relaxed distributional and dependence assumptions.  
Sufficient conditions for exact support recovery \eqref{eq:exact-recovery} are given in 
Section \ref{subsec:sufficient}.  A very general class of dependence structures characterized by the uniform relative stability concept will 
be introduced in Section \ref{subsec:URS}, to prepare us for the necessary condition in Section \ref{subsec:necessary}.
Section \ref{subsec:dense-signals} discusses the dense signal regime, and Section \ref{suppsec:numerical} illustrates the phase transition 
phenomena with numerical examples.  We begin with an overview of our results in the context of the existing literature.

\section{Contributions and related work} Consider the additive error model \eqref{eq:model-additive} with the triangular array of errors,
\begin{equation} \label{eq:error-array}
    {\cal E} = \left\{ (\epsilon_p(i))_{i=1}^p,\ p=1,2,\dots\right\},
\end{equation}
where the $\epsilon_p(i)$'s have common cumulative distribution function $F(x)=\P[\epsilon_p(i)\le x]$.
In contrast to the assumptions in Chapter \ref{chap:phase-transitions}, we only require the errors to have common marginal distributions, and allow them to have potentially arbitrary dependence.
% We will study the role of dependence in support recovery problems in Section \ref{sec:URS}.

Although our method of analysis applies to all light-tailed error distributions with rapidly varying tails (see Definition \ref{def:rapid-variation}), to be concrete and better convey the main ideas, we will focus on the class of $\mathrm{AGG}(\nu)$ laws (see Definition \ref{def:AGG}).
Extensions of the results to other error models are presented in Section \ref{suppsec:other-boundaries}.

As in Chapter \ref{chap:phase-transitions}, we assume the signals in model \eqref{eq:model-additive} to be a sparse vector $\mu = \left(\mu(i)\right)_{i=1}^p$ where the sparsity, with a few exceptions which will be explicitly stated, is parametrized as
\begin{equation} \label{eq:sparsity-parametrized}
    s = |S_p| = \lfloor p^{1 -\beta} \rfloor, % \quad \text{with } 0 < \beta \le 1 \; \text{(fixed)},
\end{equation}
with $0 < \beta \le 1$ fixed.

We assume that the non-zero entries of $\mu$ are positive and take values in the interval $\left[\underline{\Delta},\overline{\Delta}\right)\subset (0,\infty)$.
That is, $0<\underline{\Delta}\le\mu(i)<\overline{\Delta}\le+\infty$, for all $i\in S_p$.
The lower and upper bound on the signal sizes $\underline{\Delta}$ and $\overline{\Delta}$ are parametrized as
\begin{equation} \label{eq:signal-size-parametrized}
    \underline{\Delta} = \underline{\Delta}(p) = (\nu \underline{r} \log{p})^{1/\nu} \quad \text{and} \quad
    \overline{\Delta} = \overline{\Delta}(p)  = (\nu \overline{r} \log{p})^{1/\nu},
\end{equation}
with parameters $0 < \underline{r} \le \overline{r} \le +\infty$.
Notice that the parametrization now depends on the shape of the assumed error distributions $\mathrm{AGG}(\nu)$ through the parameter $\nu$.

According to Lemma \ref{lemma:risk-exact-recovery-probability}, in order to study the asymptotic behaviors of $\mathrm{risk}^{\mathrm{E}}$, it is sufficient to establish minimal conditions under which the support sets can be consistently estimated, i.e.,
\begin{equation} \label{eq:exact-recovery} 
    \P[\widehat{S}_p = S_p] \longrightarrow 1 \quad \text{as } \; p\to\infty, 
\end{equation}
where $\widehat{S}_p$ is an estimate of the true signal support set $S_p$.

@@

Several authors have studied the support recovery problem in terms of the Hamming loss and obtained minimax optimality results (see, e.g., \cite{ji2012ups, genovese2012comparison, jin2014optimality, butucea2018variable}).
% We briefly review the recent work by \cite{butucea2018variable}, whose .
In the special case of Gaussian marginals, \cite{butucea2018variable} showed that the boundary \eqref{eq:strong-classification-boundary-Gaussian} exists in a minimax sense.
That is, when the errors are \emph{independent} Gaussians, the Hamming loss cannot be made to vanish if the signal sizes fall below the boundary \eqref{eq:strong-classification-boundary-Gaussian} by any procedure. 
Conversely, if signal size falls below, the Hamming loss can be made to vanish with a specific thresholding procedure.

Unfortunately, as pointed out in Section \ref{sec:risks-relations}, vanishing Hamming loss is only sufficient, not necessary for support recovery \eqref{eq:exact-recovery}, and the latter sharp results do not carry over directly to the study of the probability of support recovery or exact support recovery risk.
More importantly, despite their elegance, these Hamming loss-minimax studies naturally reduce to the analysis of the elementary case of iid data, and is by design blind to non-trivial error-dependence structures.
This prevents us from fully exploring of the phase transition phenomena under other dependence conditions.
% This is arguably a consequence of the inherent limitation of the Hamming-loss approach. 
% For practitioners, a minimax statement in the Gaussian case seems to offer little guidance.
% Indeed, in applications, independence is an exception rather than the rule; Gaussianity of the errors may also be unnecessarily restrictive.

So far in the literature, the role of dependence, and that of the distributional assumptions in model 
\eqref{eq:model-additive} have remained largely unexplored.  This chapter offers advances in both directions, and provides a close-to-complete solution of the exact support recovery problem. (See also, Chapter \ref{chap:URS}.)
We briefly summarize our contributions next.

\medskip
In Section \ref{subsec:sufficient}, we study exact support recovery in the sense of \eqref{eq:exact-recovery} directly, under general 
distributional and dependence assumptions.  In particular, we describe the phase transition phenomena in the dependent AGG model, under the scaling described in \eqref{eq:sparsity-parametrized} and \eqref{eq:signal-size-parametrized}.
Consider the function
\begin{equation} \label{eq:strong-classification-boundary}
    g(\beta) = g_\nu(\beta) = (1 + (1 - \beta)^{1/\nu})^\nu, \quad \nu>0,
\end{equation}
which we refer to as the {\em strong classification boundary}.
In Theorem \ref{thm:sufficient} we show that, 
% under the general distributional assumptions in Section \ref{subsec:set-up}, 
if the signal sizes are above the boundary (i.e., $\underline{r}> g(\beta)$), the \ac{FWER}-controlling procedures described in Section \ref{sec:statistical-procedures} with appropriately calibrated levels achieve \emph{exact support recovery} as in \eqref{eq:exact-recovery}.

Conversely, we show in Theorem \ref{thm:necessary}, that for a surprisingly large class of dependence structures characterized by the concept of \emph{uniform relative stability} (URS, see Definition \ref{def:URS} below), when the signal size is below the boundary  (i.e., $r<g(\beta)$), no thresholding procedure can achieve the asymptotically perfect support recovery \eqref{eq:exact-recovery}. In fact,
\begin{equation} \label{eq:exact-recovery-failure}
    \mathbb{P}\left[\widehat{S}_p=S_p\right]\longrightarrow 0,\quad \mbox{ as }p\to \infty,
\end{equation}
for all $\widehat{S}_p$ in the form of \eqref{eq:thresholding-procedure}.

These two results show that the thresholding procedures obey a phase transition phenomenon in a strong, \emph{point-wise} sense over the class of URS dependence structures, and over the class of AGG$(\nu),\ \nu>0$ error distributions. 
The conclusions are fundamentally stronger and more informative than the minimax statements in the literature (see, e.g., \cite{butucea2018variable}).
The techniques developed in this here are also entirely different from those in \citet{ji2012ups} or \citet{butucea2018variable}, and transparent characterizations of the dependence conditions under which the phase transition type result holds will be established in the Chapter \ref{chap:URS} later.

@@

\medskip
The phase transition phenomena for two additional classes of error distributions with either heavier or lighter tails than the AGG distributions will be described in Section \ref{suppsec:other-boundaries}.

\medskip
To conclude this summary, we emphasize that the sharp phase transition results established in this chapter apply only to
the general class of thresholding procedures.  In Chapter \ref{chap:optimality}, we characterize the finite-sample Bayes optimal support estimation procedures.
It will turn out that in many cases the optimal procedures are in fact thresholding procedures.  This will lead to complete phase transition
results valid for all types of support estimators, for certain classes of error models. In general, however, thresholding procedures
can be sub-optimal.  This has only recently been noticed by the statistical community in the case when the errors have heavy (regularly-varying) tails. 
\citet{arias2019detection} discussed the phenomenon in approximate support recovery problems.  In this case, we also demonstrate the absence 
of a phase transition phenomenon in exact support recovery by thresholding, in Section \ref{suppsec:heavy-tailed}.

>>>>

We focus on exact support recovery problems in this chapter.
%Here, we limit ourselves to the general class of thresholding estimators but allow for nearly arbitrary error dependence structure.  
%Questions on optimality and extensions to other classes of estimators are pursued in Chapter \ref{chap:optimality}.  
As in Theorem \ref{thm:Gaussian-error-exact-boundary}, in order to study the asymptotic behaviors of $\mathrm{risk}^{\mathrm{E}}$, it is sufficient to establish minimal conditions under which the support sets can be consistently estimated, i.e.,
\begin{equation} \label{eq:exact-recovery} 
\P[\widehat{S}_p = S_p] \longrightarrow 1 \quad \text{as } \; p\to\infty, 
\end{equation}
where $\widehat{S}_p$ is an estimate of the true support set $S_p$ of a high-dimensional signal vector $\mu_p$ (recall Lemma \ref{lemma:risk-exact-recovery-probability}).

To generalize the results we obtained in Chapter \ref{chap:phase-transitions} to additive error models with relaxed distributional and dependence assumptions on the additive error array, described next.

%Sufficient conditions for exact support recovery are given in Section \ref{subsec:sufficient}.  A very general class of 
%dependence structures characterized by the uniform relative stability concept will be introduced in Section \ref{subsec:URS}, to prepare us 
%for the necessary condition in Section \ref{subsec:necessary}.
%Section \ref{subsec:dense-signals} discusses the dense signal regime, and Section \ref{suppsec:numerical} illustrates the phase transition 
%phenomena with numerical examples.  We begin with an overview of our results in the context of the existing literature.

\section{Generalizations of distributional and dependence assumptions}
Consider the additive error model \eqref{eq:model-additive} with the triangular array of errors,
\begin{equation} \label{eq:error-array}
    {\cal E} = \left\{ (\epsilon_p(i))_{i=1}^p,\ p=1,2,\dots\right\},
\end{equation}
where the $\epsilon_p(i)$'s have common cumulative distribution function $F(x)=\P[\epsilon_p(i)\le x]$.
In contrast to the assumptions in Chapter \ref{chap:phase-transitions}, we only require the errors to have common marginal distributions.
% We will study the role of dependence in support recovery problems in Section \ref{sec:URS}.

Although our method of analysis applies to all light-tailed error distributions with rapidly varying tails (see Definition \ref{def:rapid-variation}), to be concrete and better convey the main ideas, we will focus on the class of $\mathrm{AGG}(\nu)$ laws (see Definition \ref{def:AGG}).
Extensions of the results to other classes of error models are presented in Section \ref{suppsec:other-boundaries}.

This generalized distributional assumption on the error terms call for a suitable change to parametrization of the signal sizes in order to analyze the problem.
As in Chapter \ref{chap:phase-transitions}, we assume the signals in model \eqref{eq:model-additive} to be a sparse vector $\mu = \left(\mu(i)\right)_{i=1}^p$ where its sparsity, with a few exceptions which will be explicitly stated, is parametrized as
\begin{equation} \label{eq:sparsity-parametrized}
    s = |S_p| = \lfloor p^{1 -\beta} \rfloor, % \quad \text{with } 0 < \beta \le 1 \; \text{(fixed)},
\end{equation}
with $0 < \beta \le 1$ fixed.

We assume that the non-zero entries of $\mu$ are positive and take values in the interval $\left[\underline{\Delta},\overline{\Delta}\right)\subset (0,\infty)$.
That is, $0<\underline{\Delta}\le\mu(i)<\overline{\Delta}\le+\infty$, for all $i\in S_p$.
The lower and upper bound on the signal sizes $\underline{\Delta}$ and $\overline{\Delta}$ are parametrized as
\begin{equation} \label{eq:signal-size-parametrized}
    \underline{\Delta} = \underline{\Delta}(p) = (\nu \underline{r} \log{p})^{1/\nu} \quad \text{and} \quad
    \overline{\Delta} = \overline{\Delta}(p)  = (\nu \overline{r} \log{p})^{1/\nu},
\end{equation}
with parameters $0 < \underline{r} \le \overline{r} \le +\infty$.
%The signal sizes now depends on the shape of the assumed error distributions $\mathrm{AGG}(\nu)$ through the parameter $\nu$.

@@

Dependence conditions are also relaxed.
Several authors have studied the support recovery problem in terms of the Hamming loss and obtained minimax optimality results (see, e.g., \cite{ji2012ups, genovese2012comparison, jin2014optimality, butucea2018variable}).
%% We briefly review the recent work by \cite{butucea2018variable}, whose .
%In the special case of Gaussian marginals, \cite{butucea2018variable} showed that the boundary \eqref{eq:strong-classification-boundary-Gaussian} exists in a minimax sense.
%That is, when the errors are \emph{independent} Gaussians, the Hamming loss cannot be made to vanish if the signal sizes are sufficiently small by any procedure. 
%Conversely, if signal size falls below, the Hamming loss can be made to vanish with a very specific thresholding procedure.
%
%However, as pointed out in Section \ref{sec:risks-relations}, vanishing Hamming loss is only sufficient, not necessary for support recovery \eqref{eq:exact-recovery}, and results on the former do not carry over directly to the study of the exact support recovery problem.
%%More importantly, despite their elegance, these Hamming loss-minimax studies often amount to the analysis of the elementary case of iid data, and 
%%unless is by design blind to non-trivial error-dependence structures.
%%This prevents us from fully exploring of the phase transition phenomena under other dependence conditions.
%More importantly, since the Hamming loss is the same for both independent and dependent data, aforementioned Hamming loss-minimax studies amounted to the analysis of the elementary case of iid data. 
%This prevents one from fully exploring the phase transition phenomena under other dependence conditions.
%
%
%% This is arguably a consequence of the inherent limitation of the Hamming-loss approach. 
%% For practitioners, a minimax statement in the Gaussian case seems to offer little guidance.
%% Indeed, in applications, independence is an exception rather than the rule; Gaussianity of the errors may also be unnecessarily restrictive.
However, so far in the literature, the role of dependence, and that of the distributional assumptions in model \eqref{eq:model-additive} have remained largely unexplored. 
This chapter offers advances in both directions, and provides a close-to-complete solution of the exact support recovery problem. (See also, Chapter \ref{chap:URS}.)
We briefly summarize our contributions next.

\medskip
In Section \ref{subsec:sufficient}, we study exact support recovery in the sense of \eqref{eq:exact-recovery} directly, under general 
distributional and dependence assumptions.  In particular, we describe the phase transition phenomena in the dependent AGG model, under the scaling described in \eqref{eq:sparsity-parametrized} and \eqref{eq:signal-size-parametrized}.
Consider the function
\begin{equation} \label{eq:strong-classification-boundary}
    f_{\mathrm{E}}(\beta) = f_{\mathrm{E},\nu}(\beta) = (1 + (1 - \beta)^{1/\nu})^\nu, \quad \nu>0,
\end{equation}
which we refer to as the {\em strong classification boundary}.
In Theorem \ref{thm:sufficient} we show that, 
% under the general distributional assumptions in Section \ref{subsec:set-up}, 
if the signal sizes are above the boundary (i.e., $\underline{r}> f_{\mathrm{E}}(\beta)$), the \ac{FWER}-controlling procedures described in Section \ref{sec:statistical-procedures} with appropriately calibrated levels achieve \emph{exact support recovery} as in \eqref{eq:exact-recovery}.

Conversely, in Section \ref{subsec:necessary}, we show in Theorem \ref{thm:necessary} that for a surprisingly large class of dependence structures characterized by the concept of \emph{uniform relative stability} (URS, see Definition \ref{def:URS} below), when the signal size is below the boundary  (i.e., $r<f_{\mathrm{E}}(\beta)$), no thresholding procedure can achieve the asymptotically perfect support recovery \eqref{eq:exact-recovery}. In fact,
\begin{equation} \label{eq:exact-recovery-failure}
    \mathbb{P}\left[\widehat{S}_p=S_p\right]\longrightarrow 0,\quad \mbox{ as }p\to \infty,
\end{equation}
for all $\widehat{S}_p$ in the form of \eqref{eq:thresholding-procedure}.
These two results show that the thresholding procedures obey a phase transition phenomenon in a strong, \emph{point-wise} sense over the class of URS dependence structures, and over the class of AGG$(\nu),\ \nu>0$ error distributions. 
%  A transparent characterizations of the dependence conditions under which this result holds will be established in the Chapter \ref{chap:URS} later.

%The conclusions are fundamentally stronger and more informative than the minimax statements in the literature (see, e.g., \cite{butucea2018variable}).
%The techniques developed in this here are also entirely different from those in \citet{ji2012ups} or \citet{butucea2018variable}, and transparent characterizations of the dependence conditions under which the phase transition type result holds will be established in the Chapter \ref{chap:URS} later.

@@

%\medskip
%Our method of analysis is sufficiently general and can be applied to other error models. 
%The phase transition phenomena for two additional classes of error distributions with either heavier or lighter tails than the AGG distributions will be described in Section \ref{suppsec:other-boundaries}.

### 2021-04-04 5.Bayes.optimality/5.Bayes_optimality_and_minimax.tex
many changes... Chapter 4 intro WIP

\begin{corollary}[Point-wise minimax]
\label{cor:point-wise-minimax}
Let $\widehat{S}^{\text{Bonf}}$ be the sequence of Bonferroni's procedure described in Theorem \ref{thm:sufficient}. 
Let also the errors have common $\text{AGG}(\nu)$ distribution $F$ with parameter $\nu>0$, and $\Theta_p^+$ be as defined in \eqref{eq:minimax-signal-config-over}.
If $\underline{r}>g(\beta)$, then we have
\begin{equation} \label{eq:point-wise-minimax-above}
    \limsup_{p\to\infty} \sup_{\mu\in\Theta_p^+(\beta, \underline{r})} \P(\widehat{S}^{\text{Bonf}}_p \neq S_p) = 0,
\end{equation}
for arbitrary dependence structure of the error array ${\cal E} = \{\epsilon_p(i)\}_p$.
Let $\cal T$ be the class of thresholding procedures \eqref{eq:thresholding-procedure}. 
If $\underline{r}<g(\beta)$, then we have
\begin{equation} \label{eq:point-wise-minimax-below}
    \liminf_{p\to\infty} \inf_{\widehat{S}_p\in \cal T} \sup_{\mu\in\Theta_p^+(\beta, \underline{r})} \P(\widehat{S}_p \neq S_p) = 1,
\end{equation}
for any error dependence structure such that ${\cal E}\in U(F)$ and ${(-\cal E)}\in U(F)$.
\end{corollary}

@@

For the second statement \eqref{eq:point-wise-minimax-below}, since $\underline{r}<g(\beta)$, we can pick a sequence $\mu^*\in\Theta_p^+(\beta, \underline{r})$ such that $|S_p| = \lfloor p^{1-\beta}\rfloor$, with signals having the same signal size $\mu(i)=(2r\log{p})^{1/\nu}$ for all $i\in S_p$, where $\underline{r}<{r}<g(\beta)$.
For this particular choice of $\mu^*$ we have $\mu^*\in\Theta_p^-(\beta, \overline{r})$ where $r<\overline{r}<g(\beta)$,
and according to Theorem \ref{thm:necessary}, we obtain $\lim_{p\to\infty} \inf_{\widehat{S}_p\in \cal T} \mathbb P[\widehat{S}_p \neq S_p] = 1$, for all dependence structures in the URS class.
\end{proof}

@@

\begin{theorem} \label{thm:necessary-strengthened}
Consider the additive model \eqref{eq:model-additive} where the $\epsilon_p(i)$'s are independent and identically distributed with log-concave densities in the AGG class. 
Let the signals be as prescribed in Corollary \ref{c:log-concave}.
If the signal sizes fall below the strong classification boundary \eqref{eq:strong-classification-boundary}, 
i.e. $\overline{r}<g(\beta)$, then we have
\begin{equation} \label{eq:classification-impossible-Bayes}
    \liminf_{p\to\infty} \inf_{\widehat{S}_p} \E_\pi \P[\widehat{S}_p\neq S_p] = 1,
\end{equation}
where the infimum on $\widehat{S}_p$ is taken over all procedures.
\end{theorem}

\begin{proof}%[Proof of Theorem \ref{thm:necessary-strengthened}]
When the errors are independent with log-concave density, the oracle thresholding procedure $\widehat{S}^*_p$, by Corollary \ref{c:log-concave}, minimizes the Bayes risk \eqref{eq:Bayes-risk} among \emph{all} procedures. That is,
$$
\liminf_{p\to\infty} \inf_{\widehat{S}_p} \E_\pi\P[\widehat{S}_p\neq S_p]
\ge \liminf_{p\to\infty} \E_\pi\P[\widehat{S}^*_p\neq S_p].
$$
Since $\widehat{S}^*_p$ belongs to the class of all thresholding procedures, we have
\begin{align*}
    \liminf_{p\to\infty} \E_\pi\P[\widehat{S}^*_p\neq S_p] 
    &\ge \liminf_{p\to\infty} \inf_{\widehat{S}_p\in{\cal T}} \E_\pi\P[\widehat{S}_p\neq S_p] \\
    &\ge \liminf_{p\to\infty} \inf_{\widehat{S}_p\in{\cal T}} \inf_{S_p} \P[\widehat{S}_p\neq S_p] = 1,
\end{align*}
when $\overline{r}<g(\beta)$, where the last line follows from Theorem \ref{thm:necessary}.
\end{proof}

@@

\begin{corollary}
\label{cor:minimax-over-dependence}
Let $D(F)$ be the collection of error arrays with common marginal $F$ as defined in \eqref{eq:common-marginal-distribution} where $F$ is an $\text{AGG}(\nu)$ distribution.
Let also $\widehat{S}^{\text{Bonf}}_p$ be Bonferroni's procedure as described in Theorem \ref{thm:sufficient}.
If $\underline{r}>g(\beta)$, then we have
\begin{equation} \label{eq:minimax-over-dependence-over}
    \limsup_{p\to\infty} \sup_{\substack{\mu\in\Theta_p^+(\beta,\underline{r})\\ {\cal E}\in D(F)}} \P(\widehat{S}^{\text{Bonf}}_p \neq S_p) = 0.
\end{equation}
Further, when $\underline{r}<g(\beta)$, and $F$ has a positive log-concave density $f$, we have
\begin{equation} \label{eq:minimax-over-dependence-under}
    \liminf_{p\to\infty} \inf_{\widehat{S}_p} \sup_{\substack{\mu\in\Theta_p^+(\beta,\underline{r})\\ {\cal E}\in D(F)}} \P(\widehat{S}_p \neq S_p) = 
    1,
\end{equation}
where the infimum on $\widehat{S}_p$ is taken over all procedures.
\end{corollary}
\begin{proof}%[Proof of Corollary \ref{cor:minimax-over-dependence}]
Relation \eqref{eq:minimax-over-dependence-over} is a re-statement of Remark \ref{rmk:sufficient-strengthened}.

For any distribution $\pi$ (with a slight abuse of notation) over the parameter space $\Theta_p^+\times D(F)$, we have
\begin{equation} \label{eq:minimax-over-dependence-under-proof}
    \liminf_{p\to\infty} \inf_{\widehat{S}_p} \sup_{\substack{\mu\in\Theta_p^+(\beta, \underline{r})\\ {\cal E}\in D(F)}} \P(\widehat{S}_p \neq S_p) 
\ge \liminf_{p\to\infty} \inf_{\widehat{S}_p} \E_{\pi} \P(\widehat{S}_p \neq S_p),
\end{equation}
since the supremum is bounded from below by expectations.
In particular, define $\pi$ to be the uniform distribution over the configurations $\Theta_p^*\times I(f)$, where
\begin{align*}
    \Theta_p^* &=
    \{\mu\in\mathbb{R}^d:\;|S_p|=\lfloor p^{1-\beta}\rfloor,\;\mu(i)=0\;\text{for all }i\not\in S, \;\text{and}\\
    &\quad\quad\mu(i) = (\nu{r}\log{p})^{1/\nu}\;\text{for all }i\in S,\;\text{where}\;\underline{r}<r<g(\beta)\},
\end{align*}
and 
% \begin{align*}
%     I(f)&=\{{\cal E}=(\epsilon_p(i))_p:\;\epsilon_p(i)\;\text{are independently and identically distributed}\\
%     &\quad\quad\text{with density}\; f(x)\propto \exp\{-|x|^\nu/\nu\}\}.
% \end{align*}
\begin{equation*}
    I(f)=\{{\cal E}=(\epsilon_p(i))_p:\;\epsilon_p(i)\;\text{\ac{iid} with density}\; f(x)\propto \exp\{-|x|^\nu/\nu\}\}.
\end{equation*}

>>>>

\begin{corollary}[Point-wise minimax]
\label{cor:point-wise-minimax}
Let $\widehat{S}^{\text{Bonf}}$ be the sequence of Bonferroni's procedure described in Theorem \ref{thm:sufficient}. 
Let also the errors have common $\text{AGG}(\nu)$ distribution $F$ with parameter $\nu>0$, and $\Theta_p^+$ be as defined in \eqref{eq:minimax-signal-config-over}.
If $\underline{r}>f_{\mathrm{E}}(\beta)$, then we have
\begin{equation} \label{eq:point-wise-minimax-above}
    \limsup_{p\to\infty} \sup_{\mu\in\Theta_p^+(\beta, \underline{r})} \P(\widehat{S}^{\text{Bonf}}_p \neq S_p) = 0,
\end{equation}
for arbitrary dependence structure of the error array ${\cal E} = \{\epsilon_p(i)\}_p$.
Let $\cal T$ be the class of thresholding procedures \eqref{eq:thresholding-procedure}. 
If $\underline{r}<f_{\mathrm{E}}(\beta)$, then we have
\begin{equation} \label{eq:point-wise-minimax-below}
    \liminf_{p\to\infty} \inf_{\widehat{S}_p\in \cal T} \sup_{\mu\in\Theta_p^+(\beta, \underline{r})} \P(\widehat{S}_p \neq S_p) = 1,
\end{equation}
for any error dependence structure such that ${\cal E}\in U(F)$ and ${(-\cal E)}\in U(F)$.
\end{corollary}

@@

For the second statement \eqref{eq:point-wise-minimax-below}, since $\underline{r}<f_{\mathrm{E}}(\beta)$, we can pick a sequence $\mu^*\in\Theta_p^+(\beta, \underline{r})$ such that $|S_p| = \lfloor p^{1-\beta}\rfloor$, with signals having the same signal size $\mu(i)=(2r\log{p})^{1/\nu}$ for all $i\in S_p$, where $\underline{r}<{r}<f_{\mathrm{E}}(\beta)$.
For this particular choice of $\mu^*$ we have $\mu^*\in\Theta_p^-(\beta, \overline{r})$ where $r<\overline{r}<f_{\mathrm{E}}(\beta)$,
and according to Theorem \ref{thm:necessary}, we obtain $\lim_{p\to\infty} \inf_{\widehat{S}_p\in \cal T} \mathbb P[\widehat{S}_p \neq S_p] = 1$, for all dependence structures in the URS class.
\end{proof}

@@

\begin{theorem} \label{thm:necessary-strengthened}
Consider the additive model \eqref{eq:model-additive} where the $\epsilon_p(i)$'s are independent and identically distributed with log-concave densities in the AGG class. 
Let the signals be as prescribed in Corollary \ref{c:log-concave}.
If the signal sizes fall below the strong classification boundary \eqref{eq:strong-classification-boundary}, 
i.e. $\overline{r}<f_{\mathrm{E}}(\beta)$, then we have
\begin{equation} \label{eq:classification-impossible-Bayes}
    \liminf_{p\to\infty} \inf_{\widehat{S}_p} \E_\pi \P[\widehat{S}_p\neq S_p] = 1,
\end{equation}
where the infimum on $\widehat{S}_p$ is taken over all procedures.
\end{theorem}

\begin{proof}%[Proof of Theorem \ref{thm:necessary-strengthened}]
When the errors are independent with log-concave density, the oracle thresholding procedure $\widehat{S}^*_p$, by Corollary \ref{c:log-concave}, minimizes the Bayes risk \eqref{eq:Bayes-risk} among \emph{all} procedures. That is,
$$
\liminf_{p\to\infty} \inf_{\widehat{S}_p} \E_\pi\P[\widehat{S}_p\neq S_p]
\ge \liminf_{p\to\infty} \E_\pi\P[\widehat{S}^*_p\neq S_p].
$$
Since $\widehat{S}^*_p$ belongs to the class of all thresholding procedures, we have
\begin{align*}
    \liminf_{p\to\infty} \E_\pi\P[\widehat{S}^*_p\neq S_p] 
    &\ge \liminf_{p\to\infty} \inf_{\widehat{S}_p\in{\cal T}} \E_\pi\P[\widehat{S}_p\neq S_p] \\
    &\ge \liminf_{p\to\infty} \inf_{\widehat{S}_p\in{\cal T}} \inf_{S_p} \P[\widehat{S}_p\neq S_p] = 1,
\end{align*}
when $\overline{r}<f_{\mathrm{E}}(\beta)$, where the last line follows from Theorem \ref{thm:necessary}.
\end{proof}

@@

\begin{corollary}
\label{cor:minimax-over-dependence}
Let $D(F)$ be the collection of error arrays with common marginal $F$ as defined in \eqref{eq:common-marginal-distribution} where $F$ is an $\text{AGG}(\nu)$ distribution.
Let also $\widehat{S}^{\text{Bonf}}_p$ be Bonferroni's procedure as described in Theorem \ref{thm:sufficient}.
If $\underline{r}>f_{\mathrm{E}}(\beta)$, then we have
\begin{equation} \label{eq:minimax-over-dependence-over}
    \limsup_{p\to\infty} \sup_{\substack{\mu\in\Theta_p^+(\beta,\underline{r})\\ {\cal E}\in D(F)}} \P(\widehat{S}^{\text{Bonf}}_p \neq S_p) = 0.
\end{equation}
Further, when $\underline{r}<f_{\mathrm{E}}(\beta)$, and $F$ has a positive log-concave density $f$, we have
\begin{equation} \label{eq:minimax-over-dependence-under}
    \liminf_{p\to\infty} \inf_{\widehat{S}_p} \sup_{\substack{\mu\in\Theta_p^+(\beta,\underline{r})\\ {\cal E}\in D(F)}} \P(\widehat{S}_p \neq S_p) = 
    1,
\end{equation}
where the infimum on $\widehat{S}_p$ is taken over all procedures.
\end{corollary}
\begin{proof}%[Proof of Corollary \ref{cor:minimax-over-dependence}]
Relation \eqref{eq:minimax-over-dependence-over} is a re-statement of Remark \ref{rmk:sufficient-strengthened}.

For any distribution $\pi$ (with a slight abuse of notation) over the parameter space $\Theta_p^+\times D(F)$, we have
\begin{equation} \label{eq:minimax-over-dependence-under-proof}
    \liminf_{p\to\infty} \inf_{\widehat{S}_p} \sup_{\substack{\mu\in\Theta_p^+(\beta, \underline{r})\\ {\cal E}\in D(F)}} \P(\widehat{S}_p \neq S_p) 
\ge \liminf_{p\to\infty} \inf_{\widehat{S}_p} \E_{\pi} \P(\widehat{S}_p \neq S_p),
\end{equation}
since the supremum is bounded from below by expectations.
In particular, define $\pi$ to be the uniform distribution over the configurations $\Theta_p^*\times I(f)$, where
\begin{align*}
    \Theta_p^* &=
    \{\mu\in\mathbb{R}^d:\;|S_p|=\lfloor p^{1-\beta}\rfloor,\;\mu(i)=0\;\text{for all }i\not\in S, \;\text{and}\\
    &\quad\quad\mu(i) = (\nu{r}\log{p})^{1/\nu}\;\text{for all }i\in S,\;\text{where}\;\underline{r}<r<f_{\mathrm{E}}(\beta)\},
\end{align*}
and 
% \begin{align*}
%     I(f)&=\{{\cal E}=(\epsilon_p(i))_p:\;\epsilon_p(i)\;\text{are independently and identically distributed}\\
%     &\quad\quad\text{with density}\; f(x)\propto \exp\{-|x|^\nu/\nu\}\}.
% \end{align*}
\begin{equation*}
    I(f)=\{{\cal E}=(\epsilon_p(i))_p:\;\epsilon_p(i)\;\text{\ac{iid} with density}\; f(x)\propto \exp\{-|x|^\nu/\nu\}\}.
\end{equation*}
